\documentclass[runningheads]{llncs}

\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{url}
\usepackage{orcidlink}

\title{A Short Placeholder Title for an LNBIP Paper}
\titlerunning{Short Placeholder Title}

\author{Alessandro Berti\inst{1}\orcidlink{0000-0002-3279-4795} \and Humam Kourani\inst{1,2}\orcidlink{0000-0003-2375-2152} \and Wil M.P. van der Aalst\inst{1,3}\orcidlink{0000-0002-0955-6940}}
\authorrunning{Berti et al.}
\institute{Process and Data Science (PADS), RWTH Aachen University, Aachen, Germany \and
Fraunhofer Institute for Applied Information Technology FIT, Schloss Birlinghoven, 53757 Sankt Augustin, Germany \and
Celonis, Munich, Germany
\\
\email{\{a.berti, wvdaalst\}@pads.rwth-aachen.de} \\
\email{humam.kourani@fit.fraunhofer.de}}

\begin{document}
\maketitle

\begin{abstract}
This paper provides a short placeholder abstract for an LNBIP-style submission. Replace this text with the main problem, method, results, and contribution.
\keywords{Process Mining \and Placeholder \and LNBIP}
\end{abstract}

\section{Introduction}
\label{sec:introduction}
This section introduces the problem, motivation, and main contributions. Add a brief overview of the paper structure and cite relevant work such as \cite{vanDerAalst2016processmining}.

\section{Related Work}
\label{sec:relatedWork}
This section summarizes related methods, systems, and findings. Keep the comparison focused and explain the gap addressed by this paper \cite{berti2023pm4py}.

\section{Approach}
\label{sec:approach}
This section describes the proposed approach. Define the input, output, assumptions, and the main steps of the method.

\section{Implementation}
\label{sec:implementation}
This section reports implementation details, including architecture, libraries, data formats, and reproducibility information.

\section{Assessment}
\label{sec:assessment}
This section explains the evaluation setup, datasets, baselines, metrics, and main results.

\section{Discussion}
\label{sec:discussion}
This section discusses interpretation, limitations, threats to validity, and practical implications.

\section{Conclusion}
\label{sec:conclusion}
This section concludes the paper and outlines possible future work.

\begin{credits}
\subsubsection{\ackname} Funded by the European Union. This work has received funding from the European High Performance Computing Joint Undertaking (JU) and from the German Federal Ministry of Research, Technology and Space (BMFTR), the Ministry of Culture and Science of North Rhine-Westphalia (MKW NRW), and the Hessian Ministry of Science and Research, Arts and Culture (HMWK) under grant agreement No 101250682. \\
This research has been partially funded by the Federal Ministry of Research, Technology and Space (BMFTR) under grant 16IS23065. The responsibility for the content of this publication lies with the authors.
\end{credits}

\bibliographystyle{splncs04}
\bibliography{references}

\end{document}
